### 2020-02-06 README.Rmd
streamline final example in README

```{r}
most_synonyms <- taxa_tbl("col") %>% 
  group_by(acceptedNameUsageID) %>% 
  count(sort=TRUE)
most_synonyms
```
However, unlike the `filter_*` functions which return convenient in-memory tables, this is still a remote connection.  This means that direct access using the `taxa_tbl()` function (or directly accessing the database connection using `td_connect()`) is more low-level and requires greater care.  For instance, we cannot just add a `%>% mutate(acceptedNameUsage = get_names(acceptedNameUsageID))` to the above, because `get_names` does not work on a remote collection.  Instead, we would first need to use a `collect()` to pull the summary table into memory.  Users familiar with remote databases in `dplyr` will find using `taxa_tbl()` directly to be convenient and fast, while other users may find the `filter_*` approach to be more intuitive.

So which species had those 456 names?

```{r}
most_synonyms %>% 
  head(1) %>% 
  pull(acceptedNameUsageID) %>% 
  filter_id("col") %>%
  select(scientificName)
```

>>>>

```{r}
taxa_tbl("col") %>% 
  count(acceptedNameUsageID, sort=TRUE)
```

However, unlike the `filter_*` functions which return convenient in-memory tables, this is still a remote connection.  This means that direct access using the `taxa_tbl()` function (or directly accessing the database connection using `td_connect()`) is more low-level and requires greater care.  For instance, we cannot just add a `%>% mutate(acceptedNameUsage = get_names(acceptedNameUsageID))` to the above, because `get_names` does not work on a remote collection.  Instead, we would first need to use a `collect()` to pull the summary table into memory.  Users familiar with remote databases in `dplyr` will find using `taxa_tbl()` directly to be convenient and fast, while other users may find the `filter_*` approach to be more intuitive.
